A planetary collision afterglow and transit of the resultant debris cloud

### 2023-10-09 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}
\begin{centering}
%\includegraphics[width=\textwidth]{all_phot_nature_delta_flux.pdf}
\caption{Optical and infrared photometry of ASASSN-21qj.
%
Panel {\bf a} is normalised optical photometry from ASAS-SN in $V$-band and $g'$ band.
%
Panel {\bf b} shows the fractional flux increase in brightness of ASASSN-21qj in both the $W1$ and $W2$ bands, where a value of 1.0 represents the stellar contribution alone.
%
Panel {\bf c} shows the calculated $NEOWISE$ color temperature estimated from the photometry of the two bands.
%
The color temperature is plotted as zero when there is no IR excess, and is consistent with a temperature of 1000\,K while the excess is present.
%
Error bars are shown at $1\sigma$ confidence.
}
\label{fig:wisephot}
%\script{plot_all_photometry.py}
\end{centering}
\end{figure}

@@

\begin{figure*}
\begin{centering}
%\includegraphics[width=1.0\textwidth]{master_lightcurve_nature_simple.pdf}
      \caption{The light curve of ASASSN-21qj from several different photometric surveys and the derived transverse velocities.
      %
      Panel {\bf a} shows that the eclipse depth is deeper for shorter wavelengths, indicating that the transiting material is dominated by sub-micron sized grains.
      %
      Panel {\bf b} shows the  transverse velocities derived from the light curve gradients.
      %
      These are lower limits to the true velocity, and thus imply that the transiting material is closer to the star than 16\,au.
      %
      Error bars are shown at $1\sigma$ confidence.
      }
        \label{fig:eclipse_overview}
 %       \script{plot_master_lightcurve.py}
\end{centering}
\end{figure*}

@@

\begin{figure}
    \centering
%\includegraphics[width=1\textwidth]{blueing.pdf}
    \caption{Blueing of the $B-V$ colour during dimming.
    %
    Points show AAVSO data, and lines show models.
    %
    The dashed line is a line of $A_\lambda/A_V$ for the value shown in the legend in each panel, and the solid line is a model that includes an underlying scattered light component with $s=7.5$\% of the stellar flux.
    %
    Error bars are shown at $1\sigma$ confidence.
}
    \label{fig:blueing}
    %\script{blueing.py}
\end{figure}

\begin{figure}
    \centering
%\includegraphics[width=1\textwidth]{asassn-21qj-cartoon.pdf}
    \caption{Sketch of the hypothesis for the observations seen towards ASASSN-21qj.
    %
    At $t=0$, the collision occurs, producing a cloud of debris that expands and cools.
    %
    Material close to the remnant is heated by its luminosity, generating the 1000\,K infrared emission.
    %
    Around 1000 days later the expanding cloud crosses the line of sight between the star and the Earth, generating the optical light curve.}
    \label{fig:hypothesis}
    %\script{blueing.py}
\end{figure}

\begin{figure}
    \centering
%\includegraphics[width=1.0\textwidth]{final_v2_less0d029.png}
    \caption{Simulations of the formation of a post-impact body.
    %
    Giant impacts between super-Earths and mini-Neptunes can produce post-impact bodies hundreds of Earth-radii across, comparable to that required to produce the observed infrared flux. With the exception of the lower right panel, particles are colored by their material (forsterite, water, or a H$_2$-He mixture moving outwards in the initial bodies) and whether they came from the impactor or target (see top left panel). The final two panels show just the mass bound to the primary remnant which has a mass of 48.4~$M_{\rm Earth}$. In the final panel, particles that are at the minimum density imposed by the code are colored in green.}
    \label{fig:SPH}
 %   \script{fvsr.py}
\end{figure}

>>>>

\begin{figure}
\begin{centering}
\includegraphics[width=\textwidth]{figures/all_phot_nature_delta_flux.pdf}
%\includegraphics[width=1.0\textwidth]{figures/master_lightcurve_nature_simple.pdf}
\caption{Optical and infrared photometry of ASASSN-21qj.
%
Panel {\bf a} is normalised optical photometry from ASAS-SN in $V$-band and $g'$ band.
%
Panel {\bf b} shows the fractional flux increase in brightness of ASASSN-21qj in both the $W1$ and $W2$ bands, where a value of 1.0 represents the stellar contribution alone.
%
Panel {\bf c} shows the calculated $NEOWISE$ color temperature estimated from the photometry of the two bands.
%
The color temperature is plotted as zero when there is no IR excess, and is consistent with a temperature of 1000\,K while the excess is present.
%
Error bars are shown at $1\sigma$ confidence.
}
\label{fig:wisephot}
\script{plot_all_phot_nature_delta_flux.py}
%\script{plot_master_lightcurve_nature_simple.py}
\end{centering}
\end{figure}

@@

\begin{figure*}
\begin{centering}
\includegraphics[width=1.0\textwidth]{figures/master_lightcurve_nature_simple.pdf}
      \caption{The light curve of ASASSN-21qj from several different photometric surveys and the derived transverse velocities.
      %
      Panel {\bf a} shows that the eclipse depth is deeper for shorter wavelengths, indicating that the transiting material is dominated by sub-micron sized grains.
      %
      Panel {\bf b} shows the  transverse velocities derived from the light curve gradients.
      %
      These are lower limits to the true velocity, and thus imply that the transiting material is closer to the star than 16\,au.
      %
      Error bars are shown at $1\sigma$ confidence.
      }
        \label{fig:eclipse_overview}
\script{plot_master_lightcurve_nature_simple.py}
\end{centering}
\end{figure*}

@@

\begin{figure}
    \centering
\includegraphics[width=1\textwidth]{figures/blueing.pdf}
    \caption{Blueing of the $B-V$ colour during dimming.
    %
    Points show AAVSO data, and lines show models.
    %
    The dashed line is a line of $A_\lambda/A_V$ for the value shown in the legend in each panel, and the solid line is a model that includes an underlying scattered light component with $s=7.5$\% of the stellar flux.
    %
    Error bars are shown at $1\sigma$ confidence.
}
    \label{fig:blueing}
    \script{blueing.py}
\end{figure}

\begin{figure}
    \centering
\includegraphics[width=1\textwidth]{figures/asassn-21qj-cartoon.pdf}
    \caption{Sketch of the hypothesis for the observations seen towards ASASSN-21qj.
    %
    At $t=0$, the collision occurs, producing a cloud of debris that expands and cools.
    %
    Material close to the remnant is heated by its luminosity, generating the 1000\,K infrared emission.
    %
    Around 1000 days later the expanding cloud crosses the line of sight between the star and the Earth, generating the optical light curve.}
    \label{fig:hypothesis}
\end{figure}

\begin{figure}
    \centering
\includegraphics[width=1.0\textwidth]{figures/final_v2_less0d029.jpg}
    \caption{Simulations of the formation of a post-impact body.
    %
    Giant impacts between super-Earths and mini-Neptunes can produce post-impact bodies hundreds of Earth-radii across, comparable to that required to produce the observed infrared flux. With the exception of the lower right panel, particles are colored by their material (forsterite, water, or a H$_2$-He mixture moving outwards in the initial bodies) and whether they came from the impactor or target (see top left panel). The final two panels show just the mass bound to the primary remnant which has a mass of 48.4~$M_{\rm Earth}$. In the final panel, particles that are at the minimum density imposed by the code are colored in green.}
    \label{fig:SPH}
 %   \script{fvsr.py}
\end{figure}
